### 2011-06-07 thesis/novelty-intro.tex
Added related work with novelty detection. PLISS, bishop and boutell.

\subsection{Related Work}
More in line with novelty detection in scene categorization and semantic
structures, the work of \gls{PLISS}~\cite{ranganathan2010pliss}.\dots

>>>>

\subsection{Related Work}
\cite{ranganathan2010pliss} presents a system able to perform place recognition
and classification from visual clues. It is able to perform segmentation by
exploiting time-coherency on video information. The approach is particularly
interesting by its ability of keeping a fully probabilistic distribution of
the place classification and segmentation. This is, the system never performs
a deterministic decision that impacts any future , allowing it to adjust all
the segmentations and place classification as more data becomes available.
The system is also able to detect novel instances and methods how to adapt it
to run on a constant amount of memory and computation are presented.

\cite{boutell2006factor} presents a method to perform scene-classification
from low-level region detectors using factor graphs. Those low-level detectors
provide semantic (high-level) cues on the higher level scene-classification
task. Due to the nature of the low-level detectors, they ought to be treated
in a probabilistic way. For that their method uses factor graphs. The method
also exploits spatial relation information between regions to improve the
classification performance. A presented scheme using only pairwise relations
between regions is show to have better performance than try to approach the
correct scheme with a big single-factor. I.e.\ the pairwise relations can be
approximated with the modest amounts of training data, where the single-factor
demands an impractical amount of training data.
No approach is made on it at novelty detection either of regions or scene
categories.

\cite{bishop1994novelty} works shows that assuming a uniform unconditional
distribution novelty detection can be performed by triggering on the
density probability of the training data. The system is employed to detect novel
inputs for a neural-network.
